---
title: "2023-2024/25"
---

# Lecture & Computer Practical Videos

## Week 1

**Lecture video (Length: 01:00:01)**

```{r, warnings=FALSE, message=FALSE, echo=FALSE}
library(vembedr)
embed_youtube('a-HcI_VfyYI', height=400) %>% use_align('center')
```
[[**Watch on YouTube**]](https://youtu.be/a-HcI_VfyYI)

**Computer practical video (Length: 01:59:49)**

```{r, warnings=FALSE, message=FALSE, echo=FALSE}
library(vembedr)
embed_youtube('B2NGHIX5704', height=400) %>% use_align('center')
```
[[**Watch on YouTube**]](https://youtu.be/B2NGHIX5704)

## Week 2

**Lecture video (Length: 43:13)**

```{r, warnings=FALSE, message=FALSE, echo=FALSE}
library(vembedr)
embed_youtube('9ONOy4NvRPM', height=400) %>% use_align('center')
```
[[**Watch on YouTube**]](https://youtu.be/9ONOy4NvRPM)

**Computer practical video (Length: 01:59:48)**

```{r, warnings=FALSE, message=FALSE, echo=FALSE}
library(vembedr)
embed_youtube('MejBelvj7Jg', height=400) %>% use_align('center')
```
[[**Watch on YouTube**]](https://youtu.be/MejBelvj7Jg)

## Week 3

**Lecture video (Length: 01:06:42)**

```{r, warnings=FALSE, message=FALSE, echo=FALSE}
library(vembedr)
embed_youtube('znukVzQEQUQ', height=400) %>% use_align('center')
```
[[**Watch on YouTube**]](https://youtu.be/znukVzQEQUQ)

**Computer practical video (Length: 02:00:01)**

```{r, warnings=FALSE, message=FALSE, echo=FALSE}
library(vembedr)
embed_youtube('1QqA1Sqkk0A', height=400) %>% use_align('center')
```
[[**Watch on YouTube**]](https://youtu.be/1QqA1Sqkk0A)

## Week 4

**Lecture video: Not Available**

**Computer practical video (Length: 02:00:01)**

```{r, warnings=FALSE, message=FALSE, echo=FALSE}
library(vembedr)
embed_youtube('ocXeZn8WV0I', height=400) %>% use_align('center')
```
[[**Watch on YouTube**]](https://youtu.be/ocXeZn8WV0I)

## Week 5

**Lecture video (Length: 01:06:42)**

```{r, warnings=FALSE, message=FALSE, echo=FALSE}
library(vembedr)
embed_youtube('uAakkG-l-r0', height=400) %>% use_align('center')
```
[[**Watch on YouTube**]](https://youtu.be/uAakkG-l-r0)

**Computer practical video (Length 02:00:01)**

```{r, warnings=FALSE, message=FALSE, echo=FALSE}
library(vembedr)
embed_youtube('C_aGyS5Cmos', height=400) %>% use_align('center')
```
[[**Watch on YouTube**]](https://youtu.be/C_aGyS5Cmos)

## Week 6

**Lecture video (Length: 01:06:17)**

```{r, warnings=FALSE, message=FALSE, echo=FALSE}
library(vembedr)
embed_youtube('oh1IXzUu2AU', height=400) %>% use_align('center')
```
[[**Watch on YouTube**]](https://youtu.be/oh1IXzUu2AU)

**Computer practical video (Length: 02:00:01)**

```{r, warnings=FALSE, message=FALSE, echo=FALSE}
library(vembedr)
embed_youtube('Yyk1tQL1iHk', height=400) %>% use_align('center')
```
[[**Watch on YouTube**]](https://youtu.be/Yyk1tQL1iHk)

## Week 9

**Lecture video (Length: 00:41:47)**

```{r, warnings=FALSE, message=FALSE, echo=FALSE}
library(vembedr)
embed_youtube('llsnOzmJYH4', height=400) %>% use_align('center')
```
[[**Watch on YouTube**]](https://youtu.be/llsnOzmJYH4)

**Computer practical video (Length: 02:00:01)**

```{r, warnings=FALSE, message=FALSE, echo=FALSE}
library(vembedr)
embed_youtube('RnQkzPiPoSw', height=400) %>% use_align('center')
```
[[**Watch on YouTube**]](https://youtu.be/RnQkzPiPoSw)

## Week 10

**Lecture video: Not Available**

**Computer practical video (Length: 01:57:53)**

```{r, warnings=FALSE, message=FALSE, echo=FALSE}
library(vembedr)
embed_youtube('T-SgrbzisgM', height=400) %>% use_align('center')
```
[[**Watch on YouTube**]](https://youtu.be/T-SgrbzisgM)